---
title: "Electronic Resource Report"
author: "Andy Meyer"
date: "Fall 2017"
output:
  pdf_document: default
  html_document: default
---


```{r Data and Function Import, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
	message = FALSE,
	warning = FALSE)

# I could probably clean this up to import everything...
source("0 - Setup.R")
source("1a - ImportTidy - DB1.R")
source("1c - ImportTidy - Financials.R")
source("2a - Transform - DBUsage.R")
source("2b - Transform - Financials.R")
source("2c - Transform - DBCostPerUse.R")
source("4 - New Stuff.R")
```

```{r Database Set Up}
# Defining Variables for this report.
Database = "ATLA Religion Database with ATLASerials"
StartYear = 2014
EndYear = 2018
```

This is a report for `r Database` from `r StartYear` to `r EndYear`. This database is classified as a `r get.fund(Database)` database for funding purposes.

## Financial Information

```{r}
kable(cost.database.change(Database, StartYear, EndYear))
  
cost.database.graph(Database, StartYear, EndYear)
```

\newpage
## Database Usage

This section of the report shows database usage by looking at Counter Reports. 

```{r Overview Graph}

usage.graph.database(Database, StartYear, EndYear)

```


```{r}
Action = "Record Views"
```
\newpage
### Detailed Database Usage - `r Action`


```{r}

kable(usage.sum.database.acad.term(Database, StartYear, EndYear, Action))
usage.graph.database.acad.term(Database, StartYear, EndYear, Action)
```

Cost per `r Action ` is displayed below and is calculated based on the fiscal year.

```{r}

kable(cpu.database(Database, StartYear, EndYear, Action))
cpu.database.graph(Database, StartYear, EndYear, Action)

```


\newpage
```{r}
Action = "Regular Searches"
```

### Detailed Database Usage - `r Action`


```{r}

kable(usage.sum.database.acad.term(Database, StartYear, EndYear, Action))
usage.graph.database.acad.term(Database, StartYear, EndYear, Action)
```

Cost per `r Action ` is displayed below and is calculated based on the fiscal year.

```{r}

kable(cpu.database(Database, StartYear, EndYear, Action))
cpu.database.graph(Database, StartYear, EndYear, Action)

```


\newpage
```{r}
Action = "Result Clicks"
```

### Detailed Database Usage - `r Action`


```{r}

kable(usage.sum.database.acad.term(Database, StartYear, EndYear, Action))
usage.graph.database.acad.term(Database, StartYear, EndYear, Action)
```

Cost per `r Action ` is displayed below and is calculated based on the fiscal year.

```{r}

kable(cpu.database(Database, StartYear, EndYear, Action))
cpu.database.graph(Database, StartYear, EndYear, Action)

```

